---
title: "GOV 1006: Milestone 4"
subtitle: "Paper Replication"
author: "Pieter Quinton"
date: "2/28/2020"
output: 
  bookdown::pdf_document2:
    keep_tex: true
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Load in the necessary libraries with tidyverse last

library(bookdown)
library(gt)
library(stargazer)
library(tidyverse)
```

# Introduction

The paper I am replicating for my for final project is "Electoral Institutions and Electoral Cycles in Investment Incentives: A Field Experiment on Over 3,000 U.S. Municipalities" authored by Nathan M. Jensen, Micheal G. Findley, and Daniel L. Nielson (@jensen2020). The below plots are generated from the GT and Stargazer packages (@R-gt; @R-stargazer). The replication code for this milestone can be found at my github repository.^[[Github Repo](https://github.com/PGQuinton/gov1006-milestone4)]

# GT

```{r}
# I decided to use one of the preloaded datasets in R Studio, for simplicity
# The one I elected to use is mtcars

data <- mtcars

# Generated a simple gt table from the cars dataset
# Just selected the top five rows of the data and first few columns to include
# Added a source note to state where the data is from
# The car names weren't loaded as a useable column so I created a new one with the names I needed

data %>%
  head(5) %>%
   mutate(car_model = c("Mazda RX4","Mazda RX4 Wag","Datsun 710", "Hornet 4 Drive", "Hornet Sportabout")) %>%
  select(car_model, mpg:hp) %>%
  gt() %>%
    tab_header(
      title = "Car Data",
      subtitle = "Engine Analysis of Five Cars"
    ) %>%
    cols_label(
      car_model = "Car",
      mpg = "MPG",
      cyl = "Cylinders",
      disp = "Displacement",
      hp = "Horsepower"
    ) %>%
    tab_source_note(
      source_note = "The data is from the mtcars dataset, preloaded into R Studio."
    )
```


\newpage

# Stargazer

```{r, results='asis'}
model <- lm(mpg ~ cyl, data = data)

stargazer(model, 
          header = FALSE,
          title = "Relationship between MPG and Cylinders",
          covariate.labels = "cylinders",
          notes = "OLS regression using data from the preloaded mtcars dataset")
```

\newpage

# References